--- 
title: "Listen Local Collaboration Guide"
author: "Daniel Antal, CFA"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
lof: yes
classoption: openany, a4paper, oneside
papersize: a4
geometry: left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm
bibliography:
- book.bib
biblio-style: apalike
linestretch: 1.1
urlcolor: blue
linkcolor: blue
link-citations: yes
nocite: |
  @R-bookdown, @R-ggplot2, @R-kntir, @puca_intangible_2019
description: Listen Local is an open collaboration for artists, fans, managers, developers to provide alternatives to connect local audiences with local artists through locally relevant music recommendations and findings.
---

# Executive Summary {-}

Listen Local is an open collaboration for artists, fans, managers, developers to provide alternatives to connect local audiences with local artists through locally relevant music recommendations and findings. As a project of the  Digital Music Observatory it aims to make big data work for small labels and self-released artists, and to make algorithms work for and not against them.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warnings=FALSE, out.width ='80%', fig.align='center')
library(kableExtra); 
library(knitr); library(ggplot2); library(scales); library(dplyr); library(tidyr)
library(webshot)
library(here)
here::here()
```

```{r packages, include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown','kableExtra', 'webshot' ), 'packages.bib')
```

